\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{SE 3XA3: Problem Statement\\Jumbled Words}

\author{Team 08, Shunbill Jumble
		\\Shesan Balachandran, balacs1
		\\Bill Nguyen, nguyew3
		\\Muneeb Arshad, arsham14
}

\date{}

%\input{../Comments}

\begin{document}

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
Jan/27/2021 & Shesan Balachandran & Initial Draft\\
Jan/27/2021 & Bill Nguyen & Initial Draft\\
Jan/27/2021 & Muneeb Arshad & Initial Draft\\
\bottomrule
\end{tabularx}
\end{table}

\newpage

\maketitle

\section{What problem are you trying to solve?}

Many people around the world use games as an interactive method to teach kids nowadays. The jumbled word is a great way to teach children how to spell words that they know and also introduce them to new words and enrich their vocabulary. Also when learning in schools there has not been too much change in how students learn compared to many other industries and still approach learning based on tradition rather than innovation. Also, one of the most attractive features of many of the games developed in recent years is the competitive aspect to them. Because educational games are a niche market, to attract others to play such games would be to introduce a competitive aspect to them. This would make educational games more interesting and add another layer to the learning aspect.

\section{Why is this an important problem?}

With advancements in technology, things like auto correct and spell-check are taken for granted. It is still important to learn how to spell properly at a young age. This is an important problem because it provides the young generation with a more interactive and fun way to learn while enhancing their vocabulary. By deciphering jumbled words and playing through the multiple modes, it will allow children to develop logic and reasoning skills, which is much needed in many jobs and many aspects of life. To add on, the rapid advancement in the development of games has created many positives such as providing more entertainment for people all over the world but with those positives, it has also created some negative problems such as an over saturation of many games that lack educational benefits compared to many games in the past. So by creating this game we can help provide a new educational game into the market, which can give people another option to play a fun game that can also provide educational value, in a gaming market where the most popular games don’t provide this educational value.

\section{What is the context of the problem?}

The recreation and improvement upon the existing jumbled words game will provide a platform to provide a fun and interactive solution to help others learn how to spell through various game modes, and high scores and leader boards as an incentive to do their best. The environment of this problem is an educational children’s game. Jumbled Word is an app-based solution to this environmental space, and provides a rich library of words for kids and other users to practice their spelling skills but also improve their speed by completing timed game modes and competing for high scores. A progressive difficulty setting is also added as a feature to challenge the users as they get better and better at spelling. The stakeholders of this problem are the clients (The Instructor and the TA’s), the developers (our team) and the users (target audience as kids and teachers but other users who also want to improve their spelling skills or just want a casual game to play).
%\wss{comment}

%\ds{comment}

%\mj{comment}

%\cm{comment}

%\mh{comment}

\end{document}